R dyntrace report

### 2018-02-01 graphs/report.Rmd
All the graphs re-vamped, all (practical) per-package graphs implemented.

knitr::opts_chunk$set(cache=TRUE)

@@

make_graphs_for_range <- function(data, range_column, f, max.col=10) {
  graphs <- lapply(data %>% select(!!range_column) %>% distinct %>% pull(!!range_column),
                   function(x) f(data %>% filter_(paste(range_column,"==",quote(x)))))
  do.call("grid.arrange", c(graphs, ncol=min(length(graphs), max.col)))
}
```

@@

promise_full_types %>% 
  arrange(desc(number)) %>%
  mutate(number=pp_trunc(number), percent=pp_perc(percent)) %>%
  kable(col.names=c("type trace", "number", "percent"), align="lrr")
```

@@

@@

``` {r, "calls by type, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
make_graphs_for_packages(calls_types, max.col=package_figure_columns, f=function(data) function(package) {
  package_data <- 
    data %>% 
    filter(name == !!package) %>%
    group_by(type) %>% 
    summarise(number=sum(number)) %>% 
    mutate(percent=100*number/sum(number))

@@

``` {r, "functions by type, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
make_graphs_for_packages(function_types, max.col=package_figure_columns, f=function(data) function(package) {
  package_data <- 
    data %>% 
    filter(name == !!package) %>%
    group_by(type) %>% 
    summarise(number=sum(number)) %>% 
    mutate(percent=100*number/sum(number))

@@

<center>
<div class="col2">
<div class="together">
```{r, "byte-code compilation, calls", echo=FALSE, fig.width=5, fig.height=3.5, warning=FALSE}
closure_call.compilation.histogram <- load_local_csv("compiled_calls.csv") # compiled

```
</div>

```{r, "byte-code compilation, functions", echo=FALSE, fig.width=5, fig.height=3.5, warning=FALSE}
closure.function.compilation.histogram <- 
  load_local_csv("compiled_functions.csv") %>%
  group_by(compiled) %>% 
  summarise(number=sum(number)) %>% 
  mutate(percent=100*number/sum(number))

slices <- (closure.function.compilation.histogram)$number
labels <- (closure.function.compilation.histogram %>% mutate(type = ifelse(percent>1, compiled, "")))$compiled
par(mar=c(0,2,2,2))

pie(slices, labels, main="Compiled closures (functions)")
```

@@

@@

```{r, "interactions among poromises", echo=FALSE, comment="", fig.width=10, fig.height=4.5}
promises_forced_by_another_promise <-   
  load_local_csv("promises_forced_by_another_promise.csv") %>%
  group_by(forced_by_another) %>% 
  summarise(number=sum(number)) %>% 
  mutate(percent=100*number/sum(number))

g_receive <- 
  ggplot(promises_forced_by_another_promise, aes(x=forced_by_another, y=number)) + 
  geom_col() +
  scale_y_continuous(labels=pp_trunc) +
  theme(legend.position="none") +
  ylab("No. of promises") + 
  xlab("This promise forced\nby another promise")

promises_forcing_other_promises <- 
  load_local_csv("promises_forcing_other_promises.csv") %>%
  group_by(number_of_forced_promises) %>% 
  summarise(number=sum(number)) %>% 
  mutate(percent=100*number/sum(number))

promises_forcing_other_promises_small <-
  promises_forcing_other_promises %>% 
  mutate(number_of_forced_promises=ifelse(number_of_forced_promises>=3, "3+", 
                                          number_of_forced_promises)) %>%
  group_by(number_of_forced_promises) %>%
  summarise(number=sum(number)) %>% 
  mutate(percent=100*number/sum(number))

promises_forcing_other_promises_big <-
  promises_forcing_other_promises %>% 
  filter(number_of_forced_promises >= 3) %>%
  group_by(number_of_forced_promises) %>%
  summarise(number=sum(number)) %>% 
  mutate(percent=100*number/sum(number))

@@

@@

grid.arrange(g_receive, g_cause_small, g_cause_big, ncol=3, widths=c(4,5,9))
```

@@

## Strictness

```{r, "call strictnes", echo=FALSE, fig.width=10, fig.height=4.5}
strict_calls <- 
  load_local_csv("call_strictness.csv") %>%
  group_by(strict) %>% 
  summarise(number=sum(number)) %>% 
  mutate(percent=100*number/sum(number))

strict_calls_pie <-
  ggplot(strict_calls, aes(x=strict, y=number)) + 
  geom_col() +
  scale_y_continuous(labels=pp_trunc) +
  theme(legend.position="none") +
  ylab("No. of calls") + 
  xlab("Call strictness")

strict_closure_calls <- 
  load_local_csv("call_strictness_by_type.csv") %>%
  filter(type=="closure") %>%
  group_by(type, strict) %>% 
  summarise(number=sum(number)) %>% 
  mutate(percent=100*number/sum(number)) %>%
  mutate(strict=as.logical(strict))

strict_closure_calls_pie <-
  ggplot(strict_closure_calls, aes(x=strict, y=number)) + 
  geom_col() +
  scale_y_continuous(labels=pp_trunc) +
  theme(legend.position="none") +
  ylab("No. of calls") + 
  xlab("Call strictness (closures)")

strict_functions <-
  load_local_csv("function_strictness.csv") %>%
  group_by(strict) %>%
  summarise(number=sum(number)) %>%
  mutate(percent=100*number/sum(number))

strict_functions_pie <-
  ggplot(strict_functions, aes(x=strict, y=number)) +
  geom_col() +
  scale_y_continuous(labels=pp_trunc) +
  theme(legend.position="none") +
  ylab("No. of functions") +
  xlab("Function strictness")

strict_closure_functions <- 
  load_local_csv("function_strictness_by_type.csv") %>%
  filter(type=="closure") %>%
  group_by(type, strict) %>% 
  summarise(number=sum(number)) %>% 
  mutate(percent=100*number/sum(number)) %>%
  mutate(strict=as.logical(strict))

strict_closure_functions_pie <-
  ggplot(strict_closure_functions, aes(x=strict, y=number)) + 
  geom_col() +
  scale_y_continuous(labels=pp_trunc) +
  theme(legend.position="none") +
  ylab("No. of functions") + 
  xlab("Function strictness (closures)")

grid.arrange(strict_calls_pie, strict_closure_calls_pie, 
             strict_functions_pie, strict_closure_functions_pie,
             ncol=4, widths=c(1,1,1,1))
```

@@

## Call strictness ratios (dominant)

```{r, "strict calls ratio", echo=FALSE, fig.width=10, fig.height=4.5}
strict_calls_ratio <- 
  load_local_csv("call_strictness_ratio.csv") %>%
  group_by(strictness_ratio) %>% 
  summarise(number=sum(number)) %>% 
  mutate(short=ifelse(strictness_ratio=="0/0" |
                        strictness_ratio=="1/1" |
                        strictness_ratio=="2/2", 
                      as.character(strictness_ratio),
                      "other")) %>%
  mutate(percent=100*number/sum(number))

strict_calls_ratio_dominant <- 
  strict_calls_ratio %>% 
  group_by(short) %>% 
  summarize(number=sum(number)) %>%
  mutate(percent=100*number/sum(number))

ggplot(strict_calls_ratio_dominant, aes(x=short, y=number)) +
  geom_col() +
  scale_y_continuous(labels=pp_trunc) +
  theme(legend.position="none") +
  ylab("No. of calls") +
  xlab("Ratio of evaluated promises")
```

@@

## Call strictness ratios (other top 20)

```{r, "call strictness ratios, other top 20", echo=FALSE, fig.width=10, fig.height=4.5}
strict_calls_ratio_other_top20 <- 
  strict_calls_ratio %>% 
  filter(short=="other") %>% 
  arrange(desc(number)) %>%
  head(20)

@@

## Call strictness ratios (other - top 20)

```{r, "call strictness ratios, top 20", echo=FALSE, fig.width=10, fig.height=4.5}
strict_calls_ratio_other <- 
  strict_calls_ratio %>% 
  filter(short=="other") %>%
  arrange(desc(number)) %>%
  tail(-20)

ggplot(strict_calls_ratio_other, aes(x=strictness_ratio, y=number)) +
  geom_col() +
  scale_y_continuous(labels=pp_trunc) +
  theme(legend.position="none", axis.text.x=element_text(size = 5, angle=90, vjust=.5)) +
  ylab("No. of calls") +
  xlab("Ratio of evaluated promises")
```

@@

## Function strictness rate

```{r, "function strictness rate", echo=FALSE, fig.width=10, fig.height=4.5}
strict_functions_rate <- 
  load_local_csv("function_strictness_rate.csv") %>%
  group_by(strictness_rate) %>% 
  summarise(number=sum(number)) %>% 
  mutate(percent=100*number/sum(number))

ggplot(strict_functions_rate , aes(x=strictness_rate, y=number)) +
  geom_col() +
  scale_y_continuous(labels=pp_trunc) +
  scale_x_discrete(limit=c(NA, "0","(0,10〉","(10,20〉", "(20,30〉", "(30,40〉", "(40,50〉", "(50,60〉", "(60,70〉","(70,80〉","(80,90〉","(90,100)","100")) +
  theme(legend.position="none") + #, axis.text.x=element_text(angle=90, vjust=.5)) +
  ylab("No. of functions") +
  xlab("Ratio of evaluated promises [%]")
```

@@

## Evaluation order

```{r, "evaluation order", echo=FALSE, fig.width=10, fig.height=4.5}
promise_force_orders <- 
  load_local_csv("evaluation_order.csv") %>%
  group_by(no.of.force.orders) %>% 
  summarise(number=sum(number)) %>% 
  mutate(percent=100*number/sum(number))

ggplot(promise_force_orders, aes(x=no.of.force.orders, y=number)) +
  geom_col() +
  scale_y_continuous(labels=pp_trunc) +
  scale_x_discrete(limit=c(0:10,">10")) +
  theme(legend.position="none") + #, axis.text.x=element_text(angle=90, vjust=.5)) +
  ylab("No. of functions") +
  xlab("No. of force orders")
```

## Argument promise mode

TODO

<!--
<div style="font-size: 50%">
How many argument promises are default and how many are not.
</div>

{r, "x", echo=FALSE}
apm <- read.table("/home/kondziu/workspace/R-dyntrace/reports/Argument Promise Mode - argument-promise-mode.tsv", sep="\t", header=TRUE)
kable(apm, "html", col.names=c("Runnable", "All", "Default argument", "Non-default argument",
                    "Unaccounted", "% of Default Arguments",
                    "% of Non-default Arguments", "% of Unaccounted")) #%>% kable_styling(bootstrap_options = c("condensed"), font_size = 10) %>% row_spec(0, font_size = 10)

<div style="font-size: 50%; padding-top:2em">
https://docs.google.com/spreadsheets/d/1miVXUxCoeYiBR0eiCB3Ipa3KBCDw7OZ77qy7RJHFJ_8/edit#gid=333058396
</div>
-->
## Argument position laziness (top 20)

TODO
<!--
<div style="font-size: 50%; padding-top:2em">
At each argument position, how often is the argument evaluated and how often it is not.
</div>

>>>>

#knitr::opts_chunk$set(cache=TRUE)

@@

make_graphs_for_range <- function(data, range_column, f, max.col=10) {
  graphs <- lapply(data %>% select(!!range_column) %>% distinct %>% pull(!!range_column),
                   function(x) f(data %>% filter_(paste(range_column,"==",quote(x)))))
  do.call("grid.arrange", c(graphs, ncol=min(length(graphs), max.col)))
}

# hard-coded columns: number
make_graphs_by_split <- function(data, key, split="name", max_columns=10, graphing_function=NA) {
  if (is.na(graphing_function))
    graphing_function <- 
      function(package, data) 
        ggplot(data, aes_string(x=key, y="number")) + 
        geom_bar(stat="identity") +
        scale_y_continuous(
          labels=pp_trunc, 
          breaks=c(max(data$number))) +
        theme(
          axis.title.y=element_blank(),
          axis.ticks.y=element_blank(),
          axis.text.y=element_text(angle=90, size=5, vjust=.5),
          axis.text.x=element_text(angle=90, size=5, vjust=.5),
          axis.title.x=element_text(size=5),
          legend.position="none") +
        xlab(package)

  packages <- data %>% select_(split) %>% distinct %>% pull(split)
  key_range <- data %>% select_(key) %>% distinct %>% collect

  splitter <- function (package)
    graphing_function(
      package,
      data %>% 
        filter(UQ(rlang::sym(split)) == !!package) %>% 
        group_by_(key) %>%
        summarise(number=sum(number)) %>% 
        right_join(key_range, by=key) %>%
        mutate(number=ifelse(is.na(number), 0, number)))

  graphs <- lapply(packages, splitter)
  do.call("grid.arrange", c(graphs, ncol=min(max_columns, ceiling(sqrt(length(graphs))))))
}

# hard coded: percent
make_graphs_by_range <- function(data, range_column, max_columns=10, graphing_function=NA) {
  if(is.na(graphing_function))
    graphing_function <- function(data)
      ggplot(data, aes_string(range_column, "percent")) + 
      geom_violin() +
      scale_y_continuous(labels=pp_perc) +
      theme(axis.title.x=element_blank(),
            axis.title.y=element_blank(),
            legend.position="none")

  splitter <- function(x) 
    graphing_function(clean_data %>% filter_(paste(range_column, "==", quote(x))))

  range <- data %>% select_(range_column) %>% distinct %>% pull(range_column)
  clean_data <- data %>% mutate(percent = ifelse(is.na(percent), 0, percent))
  graphs <- lapply(range, splitter)
  do.call("grid.arrange", c(graphs, ncol=min(length(graphs), max_columns)))
}
```

@@

promise_full_types %>% 
  arrange(desc(number)) %>%
  mutate(number=pp_trunc(number), percent=pp_perc(percent)) %>%
  select(number, percent, type) %>%
  kable(col.names=c("number", "percent", "type trace"), align="lll")
```

@@

``` {r, "promise evaluation distance, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
range <- actual_distances %>% select(actual_distance) %>% distinct %>% pull(actual_distance)

make_graphs_for_packages(actual_distances, max.col=package_figure_columns, f=function(data) function(package) {
  package_data <- 
    data %>% 
    filter(name == !!package) %>%
    group_by(actual_distance) %>% 
    summarise(number=sum(number)) %>% 
    mutate(percent=100*number/sum(number))

  package_data <- 
    tibble(actual_distance=range) %>% 
    left_join(package_data, by="actual_distance") %>%
    mutate(
      number=ifelse(is.na(number), 0, number),
      percent=ifelse(is.na(percent), 0, percent))

  ggplot(package_data, aes(x=actual_distance, y=number)) + 
    geom_bar(stat="identity") +
    scale_y_continuous(labels=pp_trunc, breaks=c(max(package_data$number))) +
    theme(axis.title.y=element_blank(),
          axis.ticks.y=element_blank(),
          axis.text.y=element_text(angle=90, size=5, vjust=.5),
          axis.text.x=element_text(angle=90, size=5, vjust=.5),
          axis.title.x=element_text(size=5),
          legend.position="none") +
    xlab(package)
})
```

@@

``` {r, "calls by type, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
range <- calls_types %>% select(type) %>% distinct %>% pull(type)
make_graphs_for_packages(calls_types, max.col=package_figure_columns, f=function(data) function(package) {
  package_data <- 
    data %>% 
    filter(name == !!package) %>%
    group_by(type) %>% 
    summarise(number=sum(number)) %>% 
    mutate(percent=100*number/sum(number))

  package_data <- 
    tibble(type=range) %>% 
    left_join(package_data, by="type") %>%
    mutate(
      number=ifelse(is.na(number), 0, number),
      percent=ifelse(is.na(percent), 0, percent))

@@

``` {r, "functions by type, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
range <- function_types %>% select(type) %>% distinct %>% pull(type)
make_graphs_for_packages(function_types, max.col=package_figure_columns, f=function(data) function(package) {
  package_data <- 
    data %>% 
    filter(name == !!package) %>%
    group_by(type) %>% 
    summarise(number=sum(number)) %>% 
    mutate(percent=100*number/sum(number))

  package_data <- 
    tibble(type=range) %>% 
    left_join(package_data, by="type") %>%
    mutate(
      number=ifelse(is.na(number), 0, number),
      percent=ifelse(is.na(percent), 0, percent))

@@

<center>
<div class="col2">
<div class="together">
```{r, "byte-code compilation, calls", echo=FALSE, fig.width=5, fig.height=3.5, warning=FALSE}
closure_call_compilation <- load_local_csv("compiled_calls.csv")

data <- 
  closure_call_compilation %>% 
  group_by(compiled) %>% 
  summarise(number=sum(number)) %>% 
  mutate(percent=100*number/sum(number))

ggplot(data, aes(x=compiled, y=number)) + 
  geom_bar(stat="identity") +
  ylab("No. of calls") + 
  scale_y_continuous(labels=pp_trunc) +
  theme(axis.title.x=element_blank())
```
</div>

```{r, "byte-code compilation, functions", echo=FALSE, fig.width=5, fig.height=3.5, warning=FALSE}
closure_function_compilation <- load_local_csv("compiled_functions.csv")

data <- 
  closure_function_compilation %>% 
  group_by(compiled) %>% 
  summarise(number=sum(number)) %>% 
  mutate(percent=100*number/sum(number))

ggplot(data, aes(x=compiled, y=number)) + 
  geom_bar(stat="identity") +
  ylab("No. of calls") + 
  scale_y_continuous(labels=pp_trunc) +
  theme(axis.title.x=element_blank())
```

@@

## Compiled calls, distribution per package/vignette

``` {r, "byte-code compilation, calls, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=5}
make_graphs_for_range(closure_call_compilation %>% mutate(percent = ifelse(is.na(percent), 0, percent)),
  "compiled", max.col=5, f=function(data)
  ggplot(data, aes(x=compiled, y=percent)) + 
  geom_violin() +
  scale_y_continuous(labels=pp_perc) +
  theme(axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        legend.position="none")
)
```

## Compiled functions, distribution per package/vignette

``` {r, "byte-code compilation, functions, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=5}
make_graphs_for_range(closure_function_compilation %>% mutate(percent = ifelse(is.na(percent), 0, percent)),
  "compiled", max.col=5, f=function(data)
  ggplot(data, aes(x=compiled, y=percent)) + 
  geom_violin() +
  scale_y_continuous(labels=pp_perc) +
  theme(axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        legend.position="none")
)
```

## Compiled calls, separate results per package/vignette

``` {r, "compiled calls, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
range <- closure_call_compilation %>% select(compiled) %>% distinct %>% pull(compiled)
make_graphs_for_packages(closure_call_compilation, max.col=package_figure_columns, f=function(data) function(package) {
  package_data <- 
    data %>% 
    filter(name == !!package) %>%
    group_by(compiled) %>% 
    summarise(number=sum(number)) %>% 
    mutate(percent=100*number/sum(number))

  package_data <- 
    tibble(compiled=range) %>% 
    left_join(package_data, by="compiled") %>%
    mutate(
      number=ifelse(is.na(number), 0, number),
      percent=ifelse(is.na(percent), 0, percent))

  ggplot(package_data, aes(x=compiled, y=number)) + 
    geom_bar(stat="identity") +
    scale_y_continuous(labels=pp_trunc, breaks=c(max(package_data$number))) +
    theme(axis.title.y=element_blank(),
          axis.ticks.y=element_blank(),
          axis.text.y=element_text(angle=90, size=5, vjust=.5),
          axis.text.x=element_text(angle=90, size=5, vjust=.5),
          axis.title.x=element_text(size=5),
          legend.position="none") +
    xlab(package)
})
```

## Compiled functions, separate results per package/vignette

``` {r, "compiled functions, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
range <- closure_function_compilation %>% select(compiled) %>% distinct %>% pull(compiled)
make_graphs_for_packages(closure_function_compilation, max.col=package_figure_columns, f=function(data) function(package) {
  package_data <- 
    data %>% 
    filter(name == !!package) %>%
    group_by(compiled) %>% 
    summarise(number=sum(number)) %>% 
    mutate(percent=100*number/sum(number))

  package_data <- 
    tibble(compiled=range) %>% 
    left_join(package_data, by="compiled") %>%
    mutate(
      number=ifelse(is.na(number), 0, number),
      percent=ifelse(is.na(percent), 0, percent))

  ggplot(package_data, aes(x=compiled, y=number)) + 
    geom_bar(stat="identity") +
    scale_y_continuous(labels=pp_trunc, breaks=c(max(package_data$number))) +
    theme(axis.title.y=element_blank(),
          axis.ticks.y=element_blank(),
          axis.text.y=element_text(angle=90, size=5, vjust=.5),
          axis.text.x=element_text(angle=90, size=5, vjust=.5),
          axis.title.x=element_text(size=5),
          legend.position="none") +
    xlab(package)
})
```

@@

```{r, "interactions among poromises", echo=FALSE, comment="", fig.width=10, fig.height=4.5}
# Graph one
promises_forced_by_another_promise <-   
  load_local_csv("promises_forced_by_another_promise.csv")

g_receive <- 
  ggplot(promises_forced_by_another_promise %>% 
    group_by(forced_by_another) %>% 
    summarise(number=sum(number)) %>% 
    mutate(percent=100*number/sum(number)), 
  aes(x=forced_by_another, y=number)) + 
  geom_col() +
  scale_y_continuous(labels=pp_trunc) +
  theme(legend.position="none") +
  ylab("No. of promises") + 
  xlab("This promise forced\nby another promise")

# Graphs two and three
promises_forcing_other_promises <- 
  load_local_csv("promises_forcing_other_promises.csv")

promises_forcing_other_promises_summarized <- 
  promises_forcing_other_promises %>%
  group_by(number_of_forced_promises) %>% 
  summarise(number=sum(number)) %>% 
  mutate(percent=100*number/sum(number))

# Graph two
promises_forcing_other_promises_small <-
  promises_forcing_other_promises_summarized %>% 
  mutate(number_of_forced_promises=ifelse(number_of_forced_promises>=3, "3+", 
                                          number_of_forced_promises)) %>%
  group_by(number_of_forced_promises) %>%
  summarise(number=sum(number)) %>% 
  mutate(percent=100*number/sum(number))

@@

# Graph three
promises_forcing_other_promises_big <-
  promises_forcing_other_promises_summarized %>% 
  filter(number_of_forced_promises >= 3) %>%
  group_by(number_of_forced_promises) %>%
  summarise(number=sum(number)) %>% 
  mutate(percent=100*number/sum(number))

@@

# Drawing
grid.arrange(g_receive, g_cause_small, g_cause_big, ncol=3, widths=c(4,5,9))
```

@@

## Promises forced by another promise, distribution per package

``` {r, "promises forced by another promise, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=5}
make_graphs_for_range(
  promises_forced_by_another_promise %>% 
    mutate(percent = ifelse(is.na(percent), 0, percent)) %>%
    mutate(forced_by_another = ifelse(is.na(forced_by_another), "NA", forced_by_another)),
  "forced_by_another", max.col=5, f=function(data)
  ggplot(data, aes(x=forced_by_another, y=percent)) + 
  geom_violin() +
  scale_y_continuous(labels=pp_perc) +
  theme(axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        legend.position="none")
)
```

## Promises forcing other promises, distribution per package

``` {r, "promises forcing other promises, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=5}
promises_forcing_other_promises_small_per_package <-
  promises_forcing_other_promises %>% 
  mutate(number_of_forced_promises=ifelse(number_of_forced_promises>=3, "3+", 
                                          number_of_forced_promises)) %>%
  group_by(name, number_of_forced_promises) %>%
  summarise(number=sum(number), percent=sum(percent)) %>%
  ungroup

make_graphs_for_range(
  promises_forcing_other_promises_small_per_package %>% 
    mutate(percent = ifelse(is.na(percent), 0, percent)) %>%
    mutate(number_of_forced_promises = ifelse(is.na(number_of_forced_promises), "NA", number_of_forced_promises)),
  "number_of_forced_promises", max.col=5, f=function(data)
  ggplot(data, aes(x=number_of_forced_promises, y=percent)) + 
  geom_violin() +
  scale_y_continuous(labels=pp_perc) +
  theme(axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        legend.position="none")
)
```

## Promises forced by another promise, separate results per package/vignette

``` {r, "promises forced by another promise, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
range <- promises_forced_by_another_promise %>% select(forced_by_another) %>% distinct %>% pull(forced_by_another)
make_graphs_for_packages(promises_forced_by_another_promise, max.col=package_figure_columns, f=function(data) function(package) {
  package_data <- 
    data %>% 
    filter(name == !!package) %>%
    group_by(forced_by_another) %>% 
    summarise(number=sum(number)) %>% 
    mutate(percent=100*number/sum(number))

  package_data <- 
    tibble(forced_by_another=range) %>% 
    left_join(package_data, by="forced_by_another") %>%
    mutate(
      number=ifelse(is.na(number), 0, number),
      percent=ifelse(is.na(percent), 0, percent))

  ggplot(package_data, aes(x=forced_by_another, y=number)) + 
    geom_bar(stat="identity") +
    scale_y_continuous(labels=pp_trunc, breaks=c(max(package_data$number))) +
    theme(axis.title.y=element_blank(),
          axis.ticks.y=element_blank(),
          axis.text.y=element_text(angle=90, size=5, vjust=.5),
          axis.text.x=element_text(angle=90, size=5, vjust=.5),
          axis.title.x=element_text(size=5),
          legend.position="none") +
    xlab(package)
})
```

## Promises forcing other promises, separate results per package/vignette

``` {r, "promises forcing other promises, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
range <- promises_forcing_other_promises_small_per_package %>% select(number_of_forced_promises) %>% distinct %>% pull(number_of_forced_promises)
make_graphs_for_packages(promises_forcing_other_promises_small_per_package, max.col=package_figure_columns, f=function(data) function(package) {
  package_data <- 
    data %>% 
    filter(name == !!package) %>%
    group_by(number_of_forced_promises) %>% 
    summarise(number=sum(number)) %>% 
    mutate(percent=100*number/sum(number))

  package_data <- 
    tibble(number_of_forced_promises=range) %>% 
    left_join(package_data, by="number_of_forced_promises") %>%
    mutate(
      number=ifelse(is.na(number), 0, number),
      percent=ifelse(is.na(percent), 0, percent))

  ggplot(package_data, aes(x=number_of_forced_promises, y=number)) + 
    geom_bar(stat="identity") +
    scale_y_continuous(labels=pp_trunc, breaks=c(max(package_data$number))) +
    theme(axis.title.y=element_blank(),
          axis.ticks.y=element_blank(),
          axis.text.y=element_text(angle=90, size=5, vjust=.5),
          axis.text.x=element_text(angle=90, size=5, vjust=.5),
          axis.title.x=element_text(size=5),
          legend.position="none") +
    xlab(package)
})
```

# Call and function definition strictness

```{r, "call strictnes", echo=FALSE, fig.width=10, fig.height=4.5}
strictness_labeller <- function(x) 
  filter(x, number>0) %>%
  mutate(label=ifelse(is.na(strict),  
                      ifelse(type=="closure", 
                             "closure\n(no arguments)", 
                             type),  
                      ifelse(strict, 
                             paste0(type, "\n(strict)"),
                             paste0(type, "\n(non-strict)"))))

strict_closure_calls <- 
  load_local_csv("call_strictness_by_type.csv") %>%
  strictness_labeller

strict_closure_calls_aggregate <- 
  strict_closure_calls %>%
  group_by(label) %>% 
  summarise(number=sum(number)) %>% 
  mutate(percent=100*number/sum(number))

ggplot(strict_closure_calls_aggregate, aes(x=label, y=number)) + 
  ggtitle("Call strictness") +
  geom_col() +
  scale_y_continuous(labels=pp_trunc) +
  theme(legend.position="none", axis.title.x=element_blank()) +
  ylab("No. of calls") 
```

```{r, "function strictnes", echo=FALSE, fig.width=10, fig.height=4.5}
strict_closure_functions <-
  load_local_csv("function_strictness_by_type.csv") %>%
  strictness_labeller

strict_closure_functions_aggregate <-
  strict_closure_functions %>%
  group_by(label) %>%
  summarise(number=sum(number)) %>%
  mutate(percent=100*number/sum(number))

ggplot(strict_closure_functions_aggregate, aes(x=label, y=number)) +
  ggtitle("Function strictness") +
  geom_col() +
  scale_y_continuous(labels=pp_trunc) +
  theme(legend.position="none", axis.title.x=element_blank()) +
  xlab("Function strictness (closures)")
```

@@

## Call strictness, distribution per package/vignette

``` {r, "call strictness, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=3}
make_graphs_by_range(strict_closure_calls, range_column="label", max_columns=6)
```

## Function strictness, distribution per package/vignette

``` {r, "function strictness, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=3}
make_graphs_by_range(strict_closure_functions, range_column="label", max_columns=6)
```

## Call strictness, separate results per package/vignette

``` {r, "call strictness, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
make_graphs_by_split(strict_closure_calls, key="label", max_columns=package_figure_columns)
```

## Function strictness, separate results per package/vignette

``` {r, "function strictness, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
make_graphs_by_split(strict_closure_functions, key="label", max_columns=package_figure_columns)
```

# Call strictness ratio

```{r, "strict calls ratio breakdown", echo=FALSE, fig.width=10, fig.height=4.5}
# strict_calls_ratio <- load_local_csv("call_strictness_ratio.csv")
# 
# strict_calls_ratio_split_arg <- strict_calls_ratio %>% 
#   mutate(evaluated_args=lapply(strsplit(strictnesss_ratio, "/"), `[[`, 1),
#          total_args=lapply(strsplit(strictnesss_ratio, "/"), `[[`, 2))
# 
# range <- strict_calls_ratio_split_arg %>% select(total_args) %>% distinct %>% arrange(total_args) %>% top(20)
# strict_calls_
```

## Call strictness ratios

```{r, "strict calls ratio", echo=FALSE, fig.width=10, fig.height=4.5}
strict_calls_ratio <- 
  load_local_csv("call_strictness_ratio.csv")

threshold = strict_calls_ratio %>% 
  group_by(strictness_ratio) %>% 
  summarise(number=sum(number)) %>% 
  select(number) %>% 
  arrange(desc(number)) %>% 
  head(8) %>% 
  pull(number) %>% 
  min

strict_calls_ratio_labelled <- 
  strict_calls_ratio %>%
  group_by(strictness_ratio) %>% 
  summarise(number=sum(number), 
            percent=(100*number/sum(number))) %>% 
  mutate(short=ifelse(number >= threshold, 
                      as.character(strictness_ratio), 
                      "other"))

ggplot(strict_calls_ratio_labelled %>% 
    group_by(short) %>% 
    summarize(number=sum(number)),
  aes(x=short, y=number)) +
  geom_col() +
  scale_y_continuous(labels=pp_trunc) +
  theme(legend.position="none") +
  ylab("No. of calls") +
  xlab("Ratio of evaluated promises (evaluated args/total args)")
```

@@

## Call strictness ratios (top 20 within other)

```{r, "call strictness ratios, other top 20", echo=FALSE, fig.width=10, fig.height=4.5}
strict_calls_ratio_other_top20 <- 
  strict_calls_ratio_labelled %>% 
  filter(short=="other") %>% 
  arrange(desc(number)) %>%
  head(20)

@@

## Call strictness ratios (all)

```{r, "call strictness ratios, top 20", echo=FALSE, fig.width=10, fig.height=4.5}
strict_calls_ratio_labelled %>% 
  arrange(desc(number)) %>%
  select(strictness_ratio, number, percent) %>%
  kable(col.names=c( "strictness ratio", "number", "percent"), align="lll")
```

@@

# Function strictness rate

```{r, "function strictness rate", echo=FALSE, fig.width=10, fig.height=4.5}
strict_functions_rate <- load_local_csv("function_strictness_rate.csv")

ggplot(strict_functions_rate %>%
         group_by(strictness_rate) %>% 
         summarise(number=sum(number)), 
       aes(x=strictness_rate, y=number)) +
  geom_col() +
  scale_y_continuous(labels=pp_trunc) +
  scale_x_discrete(
    limit=c(NA, "0","(0,10〉","(10,20〉", "(20,30〉", "(30,40〉", 
            "(40,50〉", "(50,60〉", "(60,70〉","(70,80〉","(80,90〉",
            "(90,100)","100")) +
  theme(legend.position="none") + #, axis.text.x=element_text(angle=90, vjust=.5)) +
  ylab("No. of functions") +
  xlab("Ratio of evaluated promises [%]")
```

@@

## Function strictness rate, distribution per package/vignette

``` {r, "function strictness rate, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=3}
make_graphs_by_range(strict_functions_rate %>% mutate(strictness_rate=ifelse(is.na(strictness_rate),"NA",strictness_rate)), range_column="strictness_rate", max_columns=5)
```

## Function strictness rate, separate results per package/vignette

``` {r, "function strictness rate, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
make_graphs_by_split(strict_functions_rate, key="strictness_rate", max_columns=package_figure_columns)
```

# Evaluation order

```{r, "evaluation order", echo=FALSE, fig.width=10, fig.height=4.5}
promise_force_orders <- load_local_csv("evaluation_order.csv")

ggplot(promise_force_orders %>%
      group_by(no.of.force.orders) %>% 
      summarise(number=sum(number)) %>% 
      mutate(percent=100*number/sum(number)), 
    aes(x=no.of.force.orders, y=number)) +
  geom_col() +
  scale_y_continuous(labels=pp_trunc) +
  scale_x_discrete(limit=c(0:10,">10")) +
  theme(legend.position="none") + 
  ylab("No. of functions") +
  xlab("No. of force orders")
```

## Evaluation order, distribution per package/vignette

``` {r, "evaluation order, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=3}
make_graphs_by_range(promise_force_orders, range_column="no.of.force.orders", max_columns=4)
```

## Evaluation order, separate results per package/vignette

``` {r, "evaluation order, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
make_graphs_by_split(promise_force_orders, key="no.of.force.orders", max_columns=package_figure_columns)
```

<!--## Argument promise mode
## Argument position laziness (top 20)
## Environment access 
## Default and non-default promise arguments-->
